An Analysis of a Rising Trend in Dollar Loss in Fire Incidents With and Without Sprinkler Systems in Toronto over a decade (2011-2022)

### 2024-01-23 outputs/paper/paper.qmd
Sketches added. 01-download_data.R changed the way data was getting accessed. Paper was rerendered.

cleaned_fire_data_full$`Dollar Loss in Millions` <- cleaned_fire_data_full$`Dollar Loss` / 1000000
cleaned_fire_data_full$Year <- as.numeric(cleaned_fire_data_full$Year)

@@

y_limits <- c(0, 100)
plot1 <- ggplot(cleaned_fire_data_full, aes(x = `Year`, y = `Dollar Loss in Millions`)) + 
  geom_col(alpha = 1.5, fill = "red") + 
  ylim(y_limits) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_x_continuous(breaks = 2011:2022) +
  labs(fill = "With Sprinkler")
plot2 <- ggplot(cleaned_fire_data_none, aes(x = `Year`, y = `Dollar Loss in Millions`)) + 
  geom_col(alpha = 1.5, fill = "blue") + 
  ylim(y_limits) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_continuous(breaks = 2011:2022) +
  labs(fill = "Without Sprinkler")

grid.arrange(plot1, plot2, ncol=2)
```

>>>>

cleaned_fire_data_full$`Dollar Loss in Millions` <- cleaned_fire_data_full$`Dollar Loss` / 1000000
cleaned_fire_data_full$Year <- as.numeric(cleaned_fire_data_full$Year)
# I read more on the usage of as.numeric from ChatGPT 4, its referenced to in usage.txt.

@@

y_limits <- c(0, 100)
plot1 <- ggplot(cleaned_fire_data_full, aes(x = `Year`, y = `Dollar Loss in Millions`)) + 
  geom_col(alpha = 1.5, fill = "red") + 
  ylim(y_limits) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_x_continuous(breaks = 2011:2022) +
  labs(fill = "With Sprinkler")
plot2 <- ggplot(cleaned_fire_data_none, aes(x = `Year`, y = `Dollar Loss in Millions`)) + 
  geom_col(alpha = 1.5, fill = "blue") + 
  ylim(y_limits) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_continuous(breaks = 2011:2022) +
  labs(fill = "Without Sprinkler")
# I read on how to add two plots next to each other for comparison from ChatGPT 4, its referenced to in usage.txt.
grid.arrange(plot1, plot2, ncol=2)
```
